Examining Crowd Work and Gig Work Through The Historical Lens of Piecework

### 2017-05-06 chi/piecework/presentation/complexity.tex
various minor updates and notes from msb

\begin{frame}{Complexity}
  What kinds of problems do we mean when we talk about complexity?
  \begin{itemize}
    \item<1-> Can crowds help you write something?\\
    \scriptsize{
      \textcite{bernsteinSoylent,Kim:2014:CSI:2556288.2556986,Nebeling:2016:WCW:2858036.2858169}
    }
    \item<2-> Can crowds critique novel designs?\\
    \scriptsize{
      \textcite{yuanAlmost,fuge2014analysis}
    }
    \item<3-> Can crowds create things from whole cloth?\\
    \scriptsize{
      \textcite{KimStoria,Kim2017,Hahn:2016:KAB:2858036.2858364,Lasecki:2014:LSR:2661334.2661352}
    }
  \end{itemize}
\end{frame}

\begin{frame}{What does the crowdsourcing literature say?}
\begin{columns}
  \begin{column}{0.6\textwidth}
    \begin{itemize}
      \item Build complexity into the process
      \begin{itemize}
        \item<1> Apply CS methods to people\\
        \scriptsize{
          \textcite{crowdForgeKittur}
        }
        \item<2> Humans as computational units\\
        \scriptsize{
          \textcite{Lasecki:2014:LSR:2661334.2661352}
        }
        \item<3> Crowdsourcing workflows as function state machines\\
        \scriptsize{\textcite{latoza2014microtask}
        }
      \end{itemize}
    \end{itemize}
  \end{column}

@@

\begin{frame}{What does the piecework literature say?}
    % \begin{itemize}
      % \item
      George Airy (astronomer) used a very similar approach~\cite{grier2013computers}
      % \begin{itemize}
      %   \item Break work up so that individual tasks are simple\\
      %   Make the process \textit{itself} compile the final product.
      % \end{itemize}
    % \end{itemize}
    % \vspace{0mm}
    \begin{columns}
    \begin{column}{0.6\textwidth}
      \begin{figure}
        \includegraphics[width=\textwidth]{figures/photo/Greenwich-Observatory-computing-staff-1902.jpg}
      \end{figure}
    \end{column}

@@

\begin{frame}{George Airy --- whiz kid}
    Airy built complexity into the process, assigning \textit{human computers} 
    to compute, verify, and correct the right ascension and declination of stars.

@@

\begin{frame}\frametitle{Planes, trains, and automobiles}
             \framesubtitle{{\dots~not in that order}}

  \begin{columns}
  % \vspace{1mm}
  \only<1,4->{
  \begin{column}{0.33\textwidth}
  \centering
  Trains
  \begin{figure}
    \begin{overlayarea}{\textwidth}{4cm}
    \begin{minipage}[c][4cm]{\textwidth}
      \includegraphics[width=\textwidth]{figures/photo/train_workers.jpg}
    \end{minipage}
    \end{overlayarea}
    % \caption{i wanna fly the train}
    \end{figure}
\end{column}

\only<1>{
    \begin{column}{0.66\textwidth}
      \begin{itemize}
        \item ``Efficiency experts'' measured how long it would take to do various jobs~\cite{doi:10.2307/1883615}
        \item These measurements would be used to assign values for each specific task~\cite{american1921problem}
        \item Train engineers instituted ``The Fix'' to correct perceived unfairness~\cite{roy1954efficiency}
      \end{itemize}
    \end{column}
  }
}

@@

  \begin{column}{0.33\textwidth}
    \centering
      Automobiles
      \begin{figure}
        \begin{overlayarea}{\textwidth}{4cm}
        \begin{minipage}[c][4cm]{\textwidth}
          \includegraphics[width=\textwidth]{figures/photo/ford_assembly_line.jpg}
        \end{minipage}
        \end{overlayarea}
        % \caption{something something}
      \end{figure}
  \end{column}

@@

  \only<3->{
    \only<3>{
      \begin{column}{0.66\textwidth}
      \end{column}
    }
  \begin{column}{0.33\textwidth}
    \centering
      Planes
      \begin{figure}
        \begin{overlayarea}{\textwidth}{4cm}
        \begin{minipage}[c][4cm]{\textwidth}
            \includegraphics[width=\textwidth]{figures/photo/Rosie_the_Riveter_(Vultee)_DS.jpg}
      \end{minipage}
      \end{overlayarea}
      % \caption{i wanna fly the plane}
      \end{figure}
  \end{column}
  }

@@

\begin{frame}{Complexity}{Cab Drivers}
% \begin{columns}
  % \begin{column}{0.20\textwidth}
    % \begin{itemize}
    %   \item 
      % Cab drivers
    % \end{itemize}
  % \end{column}

  % \begin{column}{0.80\textwidth}
  \begin{figure}
  \includegraphics<1>[width=\textwidth]{figures/photo/knowledge-student.jpg}
  \includegraphics<2>[width=\textwidth]{figures/photo/gps-map.jpg}

  \end{figure}
  % \end{column}
% \end{columns}
\end{frame}

\begin{frame}{Complexity}{Algorithmic Measurement}
    notes
    \begin{itemize}
      \item I'm thinking of pointing to UpWork's screen recording tool as a way to measure workers
      \item also maybe google analytics and other ways of tracking web--based workers
    \end{itemize}
\end{frame}

>>>>

\begin{frame}{Complexity}
  What do we mean when we talk about complexity?
  \begin{itemize}
    \item<1-> Can crowds help you write something?\\
    \scriptsize{
      \textcite{bernsteinSoylent,Kim:2014:CSI:2556288.2556986,Nebeling:2016:WCW:2858036.2858169}
    }
    \item<2-> Can crowds critique novel designs?\\
    \scriptsize{
      \textcite{yuanAlmost,fuge2014analysis}
    }
    \item<3-> Can crowds create things from whole cloth?\\
    \scriptsize{
      \textcite{KimStoria,Kim2017,Hahn:2016:KAB:2858036.2858364,Lasecki:2014:LSR:2661334.2661352}
    }
  \end{itemize}
\end{frame}

\begin{frame}{What Does Crowdsourcing Say?}
\begin{columns}
  \begin{column}{0.6\textwidth}
    \begin{itemize}
      \item Build complexity into the process
      \begin{itemize}
        \item<1> Apply CS methods to people\\
        \scriptsize{
          \textcite{crowdForgeKittur}
        }
        \item<2> Humans as computational units\\
        \scriptsize{
          \textcite{Lasecki:2014:LSR:2661334.2661352}
        }
        \item<3> Crowdsourcing workflows as function state machines\\
        \scriptsize{\textcite{latoza2014microtask}
        }
      \end{itemize}
    \end{itemize}
  \end{column}

@@

\begin{frame}{What Does Piecework Say?}
    % \begin{itemize}
      % \item
      George Airy (astronomer) used a very similar approach\\
      \scriptsize{\textcite{grier2013computers}}
      % \begin{itemize}
      %   \item Break work up so that individual tasks are simple\\
      %   Make the process \textit{itself} compile the final product.
      % \end{itemize}
    % \end{itemize}
    % \vspace{0mm}
    \begin{columns}
    \begin{column}{0.6\textwidth}
      \begin{figure}
        \includegraphics[width=\textwidth]{figures/photo/Greenwich-Observatory-computing-staff-1902.jpg}
      \end{figure}
    \end{column}

@@

\begin{frame}{George Airy}
    Airy built complexity into the process, assigning \textit{human computers} 
    to compute, verify, and correct the right ascension and declination of stars.

@@

\begin{frame}{Planes, Trains, and Automobiles}
  \begin{columns}
  % \vspace{1mm}
  \only<1,4->{
  \begin{column}{0.33\textwidth}
  \centering
  Trains
  \begin{figure}
    \begin{overlayarea}{\textwidth}{4cm}
    \begin{minipage}[c][4cm]{\textwidth}
      \includegraphics[width=\textwidth]{figures/photo/train_workers.jpg}
    \end{minipage}
    \end{overlayarea}
    % \caption{i wanna fly the train}
    \end{figure}
\end{column}

\only<1>{
    \begin{column}{0.66\textwidth}
      \begin{itemize}
        \item ``Efficiency experts'' measured how long it would take to do various jobs\\
        \scriptsize{\textcite{doi:10.2307/1883615}}
        \item These measurements would be used to assign values for each specific task\\
        \scriptsize{\textcite{american1921problem}}
        \item Train engineers instituted ``The Fix'' to correct perceived unfairness\\
        \scriptsize{\textcite{roy1954efficiency}}
      \end{itemize}
    \end{column}
  }
}

@@

  \begin{column}{0.33\textwidth}
    \centering
      Automobiles
      \begin{figure}
        \begin{overlayarea}{\textwidth}{4cm}
        \begin{minipage}[c][4cm]{\textwidth}
          \includegraphics[width=\textwidth]{figures/photo/ford_assembly_line.jpg}
        \end{minipage}
        \end{overlayarea}
      \end{figure}
  \end{column}

@@

  \only<3->{
    \only<3>{
      \begin{column}{0.66\textwidth}
      \begin{itemize}
        \item Men drafted during World War II
        \item Factories turned to a new workforce who had neither conventional training nor experience
        \item Training for individual tasks and correspondingly assigning workers 
      \end{itemize}
      \end{column}
    }
  \begin{column}{0.33\textwidth}
    \centering
      Planes
      \begin{figure}
        \begin{overlayarea}{\textwidth}{4cm}
        \begin{minipage}[c][4cm]{\textwidth}
            \includegraphics[width=\textwidth]{figures/photo/Rosie_the_Riveter_(Vultee)_DS.jpg}
      \end{minipage}
      \end{overlayarea}
      \end{figure}
  \end{column}
  }

@@

\begin{frame}{Complexity} % {Cab Drivers}
% \begin{columns}
  % \begin{column}{0.20\textwidth}
    % \begin{itemize}
    %   \item 
      % Cab drivers
    % \end{itemize}
  % \end{column}

  % \begin{column}{0.80\textwidth}
  \begin{figure}
  \includegraphics<1>[width=\textwidth]{figures/photo/knowledge-student.jpg}
  \only<2>{
  \begin{columns}
  \begin{column}{0.2\textwidth}
  \includegraphics[width=\textwidth]{figures/photo/knowledge-student.jpg}
  \end{column}
  \begin{column}{0.8\textwidth}
  \includegraphics[width=\textwidth]{figures/complexity/brain_scans.png}
  \end{column}
  \end{columns}
  }
  \includegraphics<3>[width=\textwidth]{figures/photo/gps-map.jpg}
  \end{figure}
  % \end{column}
% \end{columns}
\end{frame}

\begin{frame}{Complexity} % {Algorithmic Measurement}
    notes
    \begin{itemize}
      \item I'm thinking of pointing to UpWork's screen recording tool as a way to measure workers
      \item also maybe google analytics and other ways of tracking web--based workers
    \end{itemize}
\end{frame}

### 2017-05-06 chi/piecework/presentation/introduction.tex
various minor updates and notes from msb

% \frame<1-3>[frame1]{
\begin{frame}<-2>[label=returnable]{A brief glossary}
      \begin{itemize}
        \item<1-> \alert{Crowd work}: digitally mediated \emph{information work}
        (for example, work done on Amazon Mechanical Turk, UpWork, or 99designs)~\cite{crowdworkFuture}
        \item<2-> \alert{Gig work}: digitally mediated (often \emph{physically embodied}) one--off jobs,
        such as
        {driving},
        {courier services},
        and {administrative support}~\cite{friedman2014workers,Parigi:2016:GE:3026779.3013496}
        \item<3-> \alert{Piecework}: Payment for \emph{output} rather than for \emph{time}
      \end{itemize}
\end{frame}

\begin{frame}{Open problems in on--demand work}
\begin{columns}
\begin{column}[T]{0.5\textwidth}
  \begin{itemize}%[<+>]
    \item<2,4> \textbf{\large Complexity}\\
    \scriptsize{
    \textcite{suzukiAtelier,KimStoria,yuanAlmost,Yu2016b,Nebeling:2016:WCW:2858036.2858169,Hahn:2016:KAB:2858036.2858364}
    }
    \vspace{8mm}

    \item<3> \textbf{\large Decomposition}\\
    \scriptsize{
    \textcite{sensitiveTasks,LykourentzouPersonalityMatters,Law:2016:CKC:2858036.2858144,Chang:2016:ACC:2858036.2858411,Newell:2016:OMA:2858036.2858490}
    }
    \vspace{8mm}

@@

  \end{itemize}
\end{column}

\begin{column}[T]{0.25\textwidth}
  \begin{figure}
    \centering
    \vspace{-5mm}

@@

    \vspace{5mm}
    \includegraphics[width=\textwidth]{figures/hexagonflattened.png}
    \vspace{5mm}

@@

    \visible<5->{
      \vspace{10mm}
      \includegraphics[width=\textwidth]{figures/idk.png}
    }
  \end{figure}

@@

\visible<2->{
  \small{Complexity}
  \vspace{10mm}
}

@@

\visible<3->{
  \vspace{10mm}
  \small{Decomposition}
}

@@

\begin{frame}[standout]
    What is the future of work?
\end{frame}

\begin{frame}{What is the future of work?}
    How will \alert{technology} affect the complexity of the work that on--demand workers do?

@@

\againframe<2->{returnable}

@@

\begin{frame}{Introduction}
  We hope to provide:
      \begin{itemize}
        \item A useful ontological lens for making sense of crowdsourcing and gig work (which we collectively call ``\alert{on--demand work}'') as a resurgence of \alert{piecework}.
        \item A method for making sense of contemporary phenomena through \alert{historical analysis}.
      \end{itemize}
\end{frame}

\begin{frame}{A case for comparative historical analysis}
\begin{itemize}
  \item Historical analysis isn't new
  \begin{itemize}
    \item In general\\
    \scriptsize{
      \textcite{rosenberg1994exploring,rosenberg1982inside}
    }
    \item In HCI\\
    \scriptsize{
      \textcite{Wyche2006,bodker1993historical}
    }
  \end{itemize}
  \item Still, it's an underutilized method
  \begin{itemize}
    \item Provide some basic framing for ostensibly new phenomena
    \item Theoretically ground ourselves
    \item Flesh out \emph{differences} and their implications
  \end{itemize}
\end{itemize}
\end{frame}

>>>>

% \frame<1-3>[frame1]{
\begin{frame}<-3>[label=returnable]{\only<-3>{Before We Get Started\dots}\only<4->{Old Wine in New Bottles}}
      \begin{itemize}
        \item<1-> \alert{Crowd work}: digitally mediated \emph{information work}
        (for example, work done on Amazon Mechanical Turk, UpWork, or 99designs)\\
          \scriptsize{\textcite{crowdworkFuture}}
        \item<2-> \alert{Gig work}: digitally mediated (often \emph{physically embodied}) one--off jobs,
        such as
        {driving},
        {courier services},
        and {administrative support}\\
          \scriptsize{\textcite{friedman2014workers,Parigi:2016:GE:3026779.3013496}}
        \item<3-> \alert{On--demand work}: crowd work and gig work, collectively
        \item<5-> \alert{Piecework}: Payment for \emph{output} rather than for \emph{time}
      \end{itemize}
\end{frame}

\begin{frame}{Ongoing Threads in Crowdsourcing Research}
\begin{columns}
\begin{column}[T]{0.5\textwidth}
  \begin{enumerate}%[<+>]
    \item<2,4> \textbf{\large Complexity}\\
    \scriptsize{
    \textcite{suzukiAtelier,KimStoria,yuanAlmost,Yu2016b,Nebeling:2016:WCW:2858036.2858169,Hahn:2016:KAB:2858036.2858364}
    }
    \vspace{5mm}

    \item<3> \textbf{\large Decomposition}\\
    \scriptsize{
    \textcite{sensitiveTasks,LykourentzouPersonalityMatters,Law:2016:CKC:2858036.2858144,Chang:2016:ACC:2858036.2858411,Newell:2016:OMA:2858036.2858490}
    }
    \vspace{5mm}

@@

  \end{enumerate}
\end{column}

\begin{column}[T]{0.25\textwidth}
  \begin{figure}
    \centering
    % \vspace{-5mm}
    \vspace{0mm}

@@

    \vspace{4mm}
    \includegraphics[width=\textwidth]{figures/hexagonflattened.png}
    \vspace{5mm}

@@

    \visible<5->{
      \vspace{5mm}
      \includegraphics[width=\textwidth]{figures/networkTransparency.png}
    }
  \end{figure}

@@

\visible<2->{
  \small{Complexity}
  \vspace{13mm}
}

@@

\visible<3->{
  \vspace{11mm}
  \small{Decomposition}
}

@@

\begin{frame}[standout]
    What will be the future of work?
\end{frame}

\begin{frame}{What will be the future of work?}
    How will \alert{technology} affect the complexity of the work that on--demand workers do?

@@

\againframe<4->{returnable}

@@

\begin{frame}{Introduction}
  We hope to provide:
      \begin{itemize}
        \item A useful ontological lens for making sense of on--demand work as a resurgence of \alert{piecework}.
        \item A method for making sense of contemporary phenomena through \alert{historical analysis}.
      \end{itemize}
\end{frame}

\begin{frame}{Comparative Historical Analysis}
\begin{itemize}
  \item Historical analysis isn't new
  \begin{itemize}
    \item In general\\
    \scriptsize{
      \textcite{rosenberg1994exploring,rosenberg1982inside}
    }
    \item In HCI\\
    \scriptsize{
      \textcite{Wyche2006,bodker1993historical}
    }
  \end{itemize}
  \item Still, it's an underutilized method
  \begin{itemize}
    \item Provide some basic framing for \emph{ostensibly} new phenomena
    \item \emph{Explicate} our theoretical grounding
    \item Flesh out \emph{differences} and their implications
  \end{itemize}
\end{itemize}
\end{frame}

### 2017-05-06 chi/piecework/presentation/presentation.tex
design changes
various minor updates and notes from msb

% !TEX program = lualatex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Beamer Presentation
% LaTeX Template
% Version 1.0 (10/11/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\usepackage{tikz,lmodern,textpos,hyperref,graphicx,booktabs,appendixnumberbeamer,nth,xcolor,svg,subfiles}
\usepackage[citestyle=numeric,backend=bibtex]{biblatex}
\usepackage[export]{adjustbox}
\usepackage[en-US]{datetime2}
\bibliography{references}
\usetheme{metropolis}
\beamertemplatenavigationsymbolsempty
\renewcommand\textbullet{\ensuremath{\bullet}}
\definecolor{stanfordRed}{HTML}{8C1515}
% \mode<presentation>{
  % \usetheme{metropolis}
  \usecolortheme{seagull}

@@

\newenvironment{mystepwiseitemize}{\begin{itemize}[<+-| alert@+>]}{\end{itemize}}
% Theme colors are derived from these two elements
\setbeamercolor{alerted text}{fg=Orange}
\setsansfont[BoldFont={Source Sans Pro Semibold},
              Numbers={OldStyle}]{Source Sans Pro}
\setmonofont{Source Code Pro}
% \setbeamercolor{frametitle}{bg=stanfordRed}

  % \setbeamercolor*{palette tertiary}{use=structure,fg=stanfordRed,bg=stanfordRed}
% }
% \metroset{set}
\setbeamercolor{institute in head/foot}{fg=stanfordRed}
\setbeamercovered{transparent}
\setbeamercovered{again covered={\opaqueness<1->{15}}}
% \setbeamercolor{progress bar}{fg=stanfordRed}
% \setbeamercolor{progress bar}{bg=gr}
% \setsansfont{Source Sans Pro}

\title{Examining Crowd Work and Gig Work Through The Historical Lens of Piecework}
\metroset{titleformat=smallcaps}

@@

\institute[Stanford]{Stanford University}
\date{\today}
\setbeamertemplate{itemize items}{--}

@@

% \def\labelitemi{--}

% \let\oldcite=\textcite
% \renewcommand{\textcite}[1]{\textcolor[rgb]{.2,.2,.9}{[\oldcite{#1}]}}

\newcommand{\onlyinsubfile}[1]{#1}
\begin{document}
\renewcommand{\onlyinsubfile}[1]{}
\begin{frame}
\titlepage
\end{frame}
% \setbeamercovered{transparent}

\subfile{intro.tex}

\begin{frame}[standout]
    What is the future of work?
\end{frame}

\begin{frame}{What is the future of work?}

\end{frame}

\begin{frame}{Introduction}
  We hope to provide:
      \begin{itemize}
        \item A useful ontological lens for making sense of crowdsourcing and gig work (which we collectively call ``\textit{on--demand work}'') as a resurgence of \textit{piecework}.
        \item A method for making sense of contemporary phenomena through \textit{historical analysis}.
      \end{itemize}
\end{frame}

\begin{frame}{A case for comparative historical analysis}
\begin{itemize}
  \item Historical analysis isn't new
  \begin{itemize}
    \item In general (see~\textcite{rosenberg1994exploring,rosenberg1982inside})
    \item In HCI (see~\textcite{Wyche2006,bodker1993historical})
  \end{itemize}
  % \item Still can be useful.
\end{itemize}
\end{frame}

\begin{frame}{A brief glossary}
    \begin{itemize}
      \item Crowd work: digitally mediated \textbf{information work}
      --- for example, work done on Amazon Mechanical Turk~\cite{crowdworkFuture}
      \item Gig work: digitally mediated --- but often \textbf{physically embodied} --- one--off jobs,
      such as
      \textit{driving},
      \textit{courier services},
      and \textit{administrative support}~\cite{friedman2014workers,Parigi:2016:GE:3026779.3013496}
    \end{itemize}
\end{frame}

\subfile{complexity}
% \subfile{decomposition}
% \subfile{relationships}
% \subfile{contact}

% \bibliographystyle{SIGCHI-Reference-Format}
\printbibliography{}
\end{document}

>>>>

@@

\usepackage{tikz,pgf,lmodern,textpos,hyperref,graphicx,booktabs,appendixnumberbeamer,nth,xcolor,svg,subfiles,chronosys,cancel}
\usepackage{pgfcalendar}
\usepackage{datenumber,xparse,fp}

\usetikzlibrary{arrows,automata}
\usepackage[citestyle=authoryear-comp,backend=bibtex]{biblatex}
\usepackage[export]{adjustbox}
\usepackage[en-US]{datetime2}

\bibliography{references}
\usetheme{metropolis}
\beamertemplatenavigationsymbolsempty
\definecolor{stanfordRed}{HTML}{8C1515}
\definecolor{metroBackground}{RGB}{250,250,250}

% Recent Notes from msb
% [ ] I suggest that you come out with a one sentence summary of your main thesis after 2 and before 3. “What I’m going to argue in this talk is that on-demand work is a modern instantiation of a much older phenomenon, piecework [put the word on the slide], and that we’re going to be able to use the history of piecework over the past two hundred years to shed light on several unanswered questions about the unfolding phenomenon of on-demand work.”
% [ ] This way people know what you’re winding up for in this talk
% [ ] don’t get rid of slide 5. I’m just saying put one framing sentence up front here.
% [ ] 3: these are not the canonical cites for complexity. kittur crowdforge is most famous
% [ ] 3: put the task hexagons at the top, not in between. the hierarchy I see what you’re trying to do, but it’s not really working
% [ ] When you introduce the piecework term, give several examples (with pictures) that listeners will be familiar with.
% [ ] You never stopped to equate piecework to on demand work. Why does piecework = on demand work? (in particular, because on demand work ALSO pays people per task)
% [ ] 3: your complexity example is being built out of triangles, not hexagons
% [ ] Get rid of the citation numbers, and replace it with years Alkhatib 2017, not Alkhatib [1]
% [ ] 3: I think this isn’t focused correctly. I’d get rid of this slide and ONLY motivate the complexity question. Then mention briefly that in the paper you also talk about decomposition and worker relationships, but you need 10 pages and 166 references rather than a 15 minute talk to do all that. Return to these other themes at the end of the talk and mention some short take aways from each one.
% [ ] 4: doesn’t make sense to ask “how will we reach those limits?”
% [ ] LOL at the phone ringing
% [ ] 7: the top timeline is events, the bottom is citations. change the bottom one to be events
% [ ] 8: this is WAY too late to still be doing an intro. You’re five minutes into the talk. Intro should be done by 2min.
% [ ] 12: the details here are irrelevant to complexity. why does it matter that they could be fired at will, overworked, underpaid? shouldn’t we be focusing on how piecework enabled the complexity? If it’s not important (as you say), then don’t include it. Parsimony, yay!
% [ ] 12: another example of a citation I can’t follow by watching slides
% [ ] 14: ditch the shrugging guy, he’s really weird
% [ ] 15: trains — this has nothing to do with complexity…? cut?
% [ ] 15: fordism — again, explain what this has to do with complexity? what does fordism have to do with complex outcomes? spell it out. what should we be learning from this?
% [ ] 16: technology makes complex tasks relatively trivial — this is an overly broad claim. makes SOME?
% [ ] 17: speed up The Knowledge/Gmaps example. I think it can go twice as fast and still carry as much weight

\setbeamertemplate{frametitle}
{\vskip-3pt
  \leavevmode
  \hbox{%
  \begin{beamercolorbox}[wd=\paperwidth,ht=5.8ex,dp=1ex]{frametitle}%
    \raggedright\hspace*{1em}\large{\insertframetitle}
  \end{beamercolorbox}
  }%
}
\setbeamertemplate{caption}{\raggedright\footnotesize{\insertcaption}\par}

\addtobeamertemplate{frametitle}{}{%
    \begin{textblock*}{28mm}(\paperwidth-40mm,-12mm)
      \includegraphics[height=10mm]{figures/origami-1.png}
      \includegraphics[height=10mm]{figures/origami-2.png}
      \includegraphics[height=8mm]{figures/origami-white.png}
    \end{textblock*}}

\input{timeline_code}

\DeclareCiteCommand{\eventcite}{}{\chronosevent{\thefield{year}}{\printnames{labelname}}}{}{}

@@

\newenvironment{mystepwiseitemize}{\begin{itemize}[<+-| alert@+>]}{\end{itemize}}
% Theme colors are derived from these two elements
\setbeamercolor{alerted text}{fg=Orange}
\setsansfont[BoldFont={Source Sans Pro Semibold},
              Numbers={OldStyle}]{Source Sans Pro}
\setmonofont{Source Code Pro}
\setbeamercolor{institute in head/foot}{fg=stanfordRed}
\setbeamercovered{transparent}
\setbeamercovered{again covered={\opaqueness<1->{15}}}

\title{Examining Crowd Work and Gig Work Through The Historical Lens of Piecework}
% \metroset{titleformat=smallcaps}

@@

\institute[Stanford]{Stanford University}
\date{\today}

@@

\newcommand{\onlyinsubfile}[1]{#1}
\newcommand{\notinsubfile}[1]{}
\begin{document}
\renewcommand{\onlyinsubfile}[1]{}
\renewcommand{\notinsubfile}[1]{#1}

\begin{frame}
\titlepage
\end{frame}
% \setbeamercovered{transparent}

\subfile{introduction}
\subfile{complexity}
\subfile{closing}
\subfile{contact}

% \begin{frame}[allowframebreaks]{References}
% \printbibliography{}
% \end{frame}

\end{document}
